---
title: "Page Load Analysis\nBlinkOn 8"
author: "tdresser@chromium.org"
date: "September 14, 2017"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning=FALSE)
source('main.R')
source('per_second.R')
```

## Objective
* Find Chrome and Website bugs based on new insight.
* Understand Page Load performance at scale.
* Identify weaknesses in our metrics.

## Gathering Data
* Load the Alexa top 10k on Nexus 5's.
* Simulate 3G network.
* Both warm & cold Page loads.
* Reasonably detailed main thread attribution.

## Overall Distribution

```{r, echo=FALSE, warning=FALSE}
ggplotly(plot_totals_jitter +
  theme(strip.text.x = element_text(size = 6), axis.title = element_text(margin=c(50, 50, 50, 50))), tooltip="text")
```

## Time To Consistently Interactive

```{r echo=FALSE, warning=FALSE}
ggplotly(plot_ci_warm_vs_cold, tooltip="text")
```

## Time To Consistently Interactive | Quantiles
```{r echo=FALSE, warning=FALSE}
ggplotly(plot_ci, tooltip = "text")
```

## Time To Consistently Interactive | Normalized by quantiles
```{r echo=FALSE, warning=FALSE}
ggplotly(plot_ci_normalized, tooltip="text")
```

## Per Second
```{r echo=FALSE, warning=FALSE}
ggplotly(plot_important_times, tooltip="text")
```
